Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-19 tex/v3/appendix.tex
expe

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

>>>>

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

\begin{figure*}[t]
	\centering
	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$. Note that this
	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
	also report the performance of a $1$-NN when no-adaptation is performed.  
	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor. For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
	decimation factors leads to loss of performances.
	Regarding, running time, we can note that Sinkhorn is far less efficient than
	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
	\label{fig:otda:mnist:extra}}
\end{figure*}
